Old is Still Gold: A Comparison of Cyber and Regular Consumer Fraud in The United States

### 2017-01-18 paper/paper.tex
table tweak

As the FTC dataset was aggregated for all fraud channels a major calibration step we perform is to tag each crime complaint as either cyber or regular. An associated challenge for this was our limited view of the fraud description. To perform this calibration we use the \textbf{Contact Method} and \textbf{Fraud Description} fields from Table \ref{ftcdata}. We flag a complaint as cyber if the victims primary contact method was through online media, these are primarily websites, social networks, email and IM. For the remainder of the complaints we look at the description. If the complaint description involves something associated with Internet, we classify it as a cyber fraud regardless of how the victim was initially approached. Figure \ref{classify} provides an depiction of our classification methodology. This process  provides us with two distinct categories  and enables a fair comparison of the frauds.

@@

\begin{table*}[h]
\noindent
\centering
\begin{tabular}{c||c|c|c||c|c|c}
\hline
\multicolumn{1}{c||}{\bfseries } & \multicolumn{3}{c||}{\bfseries Cyber Complaints} & \multicolumn{3}{c}{\bfseries Regular Complaints}\\
\hline
\bfseries Observed Variable & \bfseries Coefficient & \bfseries \emph{p-value} & \bfseries 95\% Confidence Interval & \bfseries Coefficient & \bfseries \emph{p-value} & \bfseries 95\% Confidence Interval \\
\hline
White (Non-Hispanic) & -0.0042 & 0.074 & [-0.009, 0] & -0.0013 &  0.128 & [0.003,  0]\\
\hline
Black & -0.0058 & 0.017 & [-0.011, -0.001] & 0.0017 & 0.054 & [-2.77$^{-5}$, -0.003]\\
\hline
Asian & -0.0025 & 0.468 & [-0.009, 0.004] & -0.0051 & 0.00 & [-0.008, -0.003]\\
\hline
Hispanic & -0.0026 & 0.014 & [-0.05, -0.001] & -0.0054 & 0.00 & [-0.006, -0.005]\\
\hline
Age & 0.0064 & 0.023 & [ 0.001, 0.012] & 0.0281 & 0.00 & [0.026, 0.030]\\
\hline
Income & -2.226$^{-6}$ & 8.85$^{-7}$ & [-3.96$^{-6}$ , -4.92$^{-7}$] & -3.695$^{-6}$ & 0.000  & [-4.31$^{-6}$, -3.08$^{-6}$]\\
\hline
Education & 0.0155 & 0.000 & [0.013, 0.018] & 0.0044 & 0.00 & [0.003, -0.005]\\
\hline
Unemployment & 0.0084 & 0.111 & [-0.002, 0.019] & -0.0028 & 0.138 & [-0.006, 0.001]\\
\hline
\end{tabular}

>>>>

As the FTC dataset was aggregated for all fraud channels a major calibration step we perform is to tag each crime complaint as either cyber or regular. An associated challenge for this was our limited view of the fraud description. To perform this calibration we use the \textbf{Contact Method} and \textbf{Fraud Description} fields from Table \ref{ftcdata}. We flag a complaint as cyber if the victims primary contact method was through online media, these are primarily websites, social networks, email and IM. For the remainder of the complaints we look at the description. If the complaint description involves something associated with Internet, we classify it as a cyber fraud regardless of how the victim was initially approached. Figure \ref{classify} provides a depiction of our classification methodology. This process  provides us with two distinct categories  and enables a fair comparison of the frauds.

@@

\begin{table*}[h]
\noindent
\centering
\begin{tabular}{c||c|c|c||c|c|c}
\hline
\multicolumn{1}{c||}{\bfseries } & \multicolumn{3}{c||}{\bfseries Cyber Complaints Per Capita} & \multicolumn{3}{c}{\bfseries Regular Complaints Per Capita}\\
\hline
\bfseries Observed Variable & \bfseries Coefficient & \bfseries \emph{p-value} & \bfseries 95\% Confidence Interval & \bfseries Coefficient & \bfseries \emph{p-value} & \bfseries 95\% Confidence Interval \\
\hline
\% White (Non-Hispanic) & -0.0042 & 0.074 & [-0.009, 0] & -0.0013 &  0.128 & [0.003,  0]\\
\hline
\% Black & -0.0058 & 0.017 & [-0.011, -0.001] & 0.0017 & 0.054 & [-2.77$^{-5}$, -0.003]\\
\hline
\% Asian & -0.0025 & 0.468 & [-0.009, 0.004] & -0.0051 & 0.00 & [-0.008, -0.003]\\
\hline
\% Hispanic & -0.0026 & 0.014 & [-0.05, -0.001] & -0.0054 & 0.00 & [-0.006, -0.005]\\
\hline
Age & 0.0064 & 0.023 & [ 0.001, 0.012] & 0.0281 & 0.00 & [0.026, 0.030]\\
\hline
Income & -2.226$^{-6}$ & 8.85$^{-7}$ & [-3.96$^{-6}$ , -4.92$^{-7}$] & -3.695$^{-6}$ & 0.000  & [-4.31$^{-6}$, -3.08$^{-6}$]\\
\hline
Education & 0.0155 & 0.000 & [0.013, 0.018] & 0.0044 & 0.00 & [0.003, -0.005]\\
\hline
Unemployment & 0.0084 & 0.111 & [-0.002, 0.019] & -0.0028 & 0.138 & [-0.006, 0.001]\\
\hline
\end{tabular}
